Title here

### 2020-03-27 tex/ms.tex
woot

%
\section{Introduction}
%
Intro here \citep{Luger2019}.
Here's an equation with a proof:
%
\begin{proof}{dummy}
    \label{eq:dummy}
    1 + 1 = 2.
\end{proof}
The proof is a Jupyter notebook with a formal derivation of the solution,
an informal justification, a numerical validation, or whatever you want it
to be.
%
And here's a figure with a link:
%
\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.5\linewidth]{figures/dummy.pdf}
    \oscaption{pretty_function}{%
        This is a plot of a pretty function. And at the end of this
        caption is a symbol with a link to the \emph{exact} script
        that generated it, hosted on \textsf{GitHub}.
        \label{fig:dummy}
    }
    \end{centering}
\end{figure}

@@

\subsection{The integral $\mathcal{J}$}
%
\begin{align}
    \label{eq:J}
    \mathcal{J}_v(k, \kap) = 
        \int_{\frac{\kappa_i}{2}}^{\frac{\kappa_{i+1}}{2}}
        \sin^{2v}\varphi
        \left(1 - \kmt\sin^2\varphi\right)^\frac{3}{2} 
        \mathrm{d}\varphi
\end{align}
%
Given the lower boundary condition
%
\begin{proof}{J0}
    \label{eq:J0}
    \mathcal{J}_0(k, \kap) &= 
        \frac{1}{3} \bigg(
            2 (2 - \kmt) \Delta \mathbf{E}(k, \kap) + 
            (\kmt - 1) \Delta \mathbf{F}(k, \kap) + 
            \kmt \Delta \mathbf{z}(k, \kap)
        \bigg)
%
    \nonumber \\
%
    \mathbf{z}(k, \boldsymbol{\kappa}) &= 
        \sin\left(\frac{\kap}{2}\right) 
        \cos\left(\frac{\kap}{2}\right) 
        \sqrt{1 - \kmt \sin^2\left(\frac{\kap}{2}\right)}
\end{proof}
%
and an upper boundary condition $\mathcal{J}_N$ 
(computed by numerical integration of Equation~\ref{eq:J}),
the values of all intermediate $J_v$ can be obtained by solving the following
tridiagonal problem:
%
\begin{proof}{Jtri}
    \label{eq:Jtri}
    \begin{pmatrix}
        a_0   & 1     &       &       &       &       \\
        b_1   & a_1   & 1     &       &       &       \\
            & b_2   & a_2   & 1     &       &       \\
            &       & b_0   & a_3   & 1     &       \\
            &       &       & \ddots& \ddots&\ddots \\
            &       &       &       & b_N   & a_N   
    \end{pmatrix}
    \begin{pmatrix}
        \mathcal{J}_1 \\
        \mathcal{J}_2 \\
        \mathcal{J}_3 \\
        \mathcal{J}_4 \\
        \cdot\cdot\cdot \\
        \mathcal{J}_{N-1}
    \end{pmatrix}
    =
    \begin{pmatrix}
        c_0 - b_0 \mathcal{J}_0 \\
        c_1 \\
        c_2 \\
        c_3 \\
        \cdot\cdot\cdot \\
        c_N - \mathcal{J}_N
    \end{pmatrix}
\end{proof}
%
where the recursion coefficients are given by
%
\begin{proof}{Jtri}
    \label{eq:Jtri_coeffs}
    a_v(k) &= -2\frac{(v + 1) + (v - 1) k^2}{2v + 3} \nonumber \\
    b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
    c_v(k, \kap) &= \frac{\Delta \mathbf{q_v}(k, \kap)}{2v + 3} \nonumber \\
    \mathbf{q_v}(k, \kap) &= 
        k^2 
        \sin^{2v + 1}\left(\frac{\kap}{2}\right) 
        \cos\left(\frac{\kap}{2}\right) 
        \bigg(1 - \kmt \sin^2\left(\frac{\kap}{2}\right)\bigg)^\frac{5}{2}
\end{proof}

>>>>

%
\section{Introduction}
%
This is an extension of \citep{Luger2019}.

%
\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/speed.pdf}
    \oscaption{speed}{%
        Evaluation time for the starry algorithm.
        \label{fig:speed}
    }
    \end{centering}
\end{figure}

@@

\subsection{The integral $\mathcal{J}$}
%
\begin{align}
    \label{eq:J}
    \mathcal{J}_v(k, \kap) = 
        \int_{\frac{\kappa_i}{2}}^{\frac{\kappa_{i+1}}{2}}
        \sin^{2v}\varphi
        \left(1 - \kmt\sin^2\varphi\right)^\frac{3}{2} 
        \mathrm{d}\varphi
\end{align}
%
Given the lower boundary condition
%
\begin{proof}{J0}
    \label{eq:J0}
    \mathcal{J}_0(k, \kap) &= 
        \frac{1}{3} \bigg(
            2 (2 - \kmt) \Delta \mathbf{E}(k, \kap) + 
            (\kmt - 1) \Delta \mathbf{F}(k, \kap) + 
            \kmt \Delta \mathbf{z}(k, \kap)
        \bigg)
%
    \nonumber \\
%
    \mathbf{z}(k, \boldsymbol{\kappa}) &= 
        \sin\left(\frac{\kap}{2}\right) 
        \cos\left(\frac{\kap}{2}\right) 
        \sqrt{1 - \kmt \sin^2\left(\frac{\kap}{2}\right)}
\end{proof}
%
and an upper boundary condition $\mathcal{J}_N$ 
(computed by numerical integration of Equation~\ref{eq:J}),
the values of all intermediate $J_v$ can be obtained by solving the following
tridiagonal problem:
%
\begin{proof}{Jtri}
    \label{eq:Jtri}
    \begin{pmatrix}
        a_0   & 1     &       &       &       &       \\
        b_1   & a_1   & 1     &       &       &       \\
            & b_2   & a_2   & 1     &       &       \\
            &       & b_0   & a_3   & 1     &       \\
            &       &       & \ddots& \ddots&\ddots \\
            &       &       &       & b_N   & a_N   
    \end{pmatrix}
    \begin{pmatrix}
        \mathcal{J}_1 \\
        \mathcal{J}_2 \\
        \mathcal{J}_3 \\
        \mathcal{J}_4 \\
        \cdot\cdot\cdot \\
        \mathcal{J}_{N-1}
    \end{pmatrix}
    =
    \begin{pmatrix}
        c_0 - b_0 \mathcal{J}_0 \\
        c_1 \\
        c_2 \\
        c_3 \\
        \cdot\cdot\cdot \\
        c_N - \mathcal{J}_N
    \end{pmatrix}
\end{proof}
%
where the recursion coefficients are given by
%
\begin{proof}{Jtri}
    \label{eq:Jtri_coeffs}
    a_v(k) &= -2\frac{(v + 1) + (v - 1) k^2}{2v + 3} \nonumber \\
    b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
    c_v(k, \kap) &= \frac{\Delta \mathbf{q}_v(k, \kap)}{2v + 3} \nonumber \\
    \mathbf{q}_v(k, \kap) &= 
        k^2 
        \sin^{2v + 1}\left(\frac{\kap}{2}\right) 
        \cos\left(\frac{\kap}{2}\right) 
        \bigg(1 - \kmt \sin^2\left(\frac{\kap}{2}\right)\bigg)^\frac{5}{2}
\end{proof}
